What's she talking about? Category based discourse inferences in early childhood

### 2020-08-12 paper/supplementary_material.Rmd
revision 1

p2 <- ggplot() +
  geom_hline(yintercept = 1/3, lty=2, size = 1)+
  geom_jitter(data = pexs_1,aes(x = age_num, y= correct, col = condition), width = .00, height = .01, alpha = .5)+
  geom_line(data = sample2, aes(x = age, y = y, col = condition, group = sample), size = .025)+
  geom_line(data = map_model_2, aes(x = age, y = y, col = condition), size = 1)+
  #geom_smooth(data = ex2_data,aes(x = age_num, y= correct, col = condition), method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, size = 1.5 )+
  geom_pointrange(data = pexs_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)+
  scale_color_manual(name = "Input",
                   breaks = c("low_input", "high_input"),
                   labels = c("Low", "High"),
                   values = c("#CC6677", "#DDCC77"))+
  theme(legend.position = "right")
```

@@

cp2 <- ggplot() +
  geom_hline(yintercept = 1/3, lty=2)+
  geom_line(data = con_sample, aes(x = age, y = y, col = Category, group = sample), size = .01, alpha = .5)+
  geom_line(data = map_con, aes(x = age, y = y, col = Category), size = 1)+
  #geom_pointrange(data = pex3_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+
  scale_color_colorblind(name = "Category")+
  theme(legend.position = "right")

>>>>

p2 <- ggplot() +
  geom_hline(yintercept = 1/3, lty=2, size = 1)+
  geom_jitter(data = pexs_1,aes(x = age_num, y= correct, col = condition), width = .00, height = .01, alpha = .5)+
  geom_line(data = sample2, aes(x = age, y = y, col = condition, group = sample), alpha = .05)+
  geom_line(data = map_model_2, aes(x = age, y = y, col = condition), size = 1)+
  #geom_smooth(data = ex2_data,aes(x = age_num, y= correct, col = condition), method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, size = 1.5 )+
  geom_pointrange(data = pexs_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)+
  scale_color_manual(name = "Input",
                   breaks = c("low_input", "high_input"),
                   labels = c("Low", "High"),
                   values = c("#CC6677", "#DDCC77"))+
  theme(legend.position = "right")
```

@@

cp2 <- ggplot() +
  geom_hline(yintercept = 1/3, lty=2)+
  geom_line(data = con_sample, aes(x = age, y = y, col = Category, group = sample), alpha = .01)+
  geom_line(data = map_con, aes(x = age, y = y, col = Category), size = 1)+
  #geom_pointrange(data = pex3_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+
  scale_color_colorblind(name = "Category")+
  theme(legend.position = "right")
